\begin{frame}
\frametitle{Conclusion}

\begin{columns}
    \begin{column}{0.5\textwidth}
        \textbf{Key Contributions:}
        \begin{itemize}
            \item Enhanced the RAST framework by introducing the Idempotency Loss.
            \item Demonstrated that Idempotency Loss ensures consistent and reliable style transfer across multiple applications.
        \end{itemize}
        
        \textbf{Insights:}
        \begin{itemize}
            \item Other proposed modifications, such as adapting multirestoration loss for low-resolution images and architectural simplifications, did not yield the desired improvements.
            \item Idempotency Loss stands out as a significant advancement in ensuring stability and consistency in style transfer.
        \end{itemize}
    \end{column}
    
    \begin{column}{0.5\textwidth}
        \textbf{Future Work:}
        \begin{itemize}
            \item Further refine the Idempotency Loss mechanism for enhanced performance.
            \item Explore alternative approaches to improve low-resolution stylization.
            \item Investigate additional architectural optimizations to build upon the strengths of Idempotency Loss.
        \end{itemize}
        
        \textbf{Final Thoughts:}
        \begin{itemize}
            \item This study provides a clear pathway for developing more robust and consistent arbitrary style transfer models, with Idempotency Loss being a pivotal component.
        \end{itemize}
    \end{column}
\end{columns}

\end{frame}
